\section{Test Cases}
\subsection{Music Player}
\story{Play .mp3 files.}{High}
{As a user, I, want to listen to the .mp3 files stored on my device.}
{\begin{itemize}
\item I am able to play a .mp3 file stored on the device.
\item I am able to regulate the volume when listening to the song.
\item I am not able to open other file types than .mp3.
\end{itemize}}

\begin{itemize}
\item Precondition: 
\subitem The application has launched the MusicPlayer Activity, and is ready to play.

\item Procedure:
\subitem Press the \texttt{Play} button.
\subitem Press the \texttt{Volume Up} button.
\subitem Press the \texttt{Volume Down} button.

\item Postcondition:
\subitem The application now plays music, which has been at different volumes.
\end{itemize}

\rule{\textwidth}{1pt}

\story{Locate .mp3 files on device.}{High}
{As a user, I, want the application to search the directories I specify for .mp3 files.}
{\begin{itemize}
\item When I start the application, it finds the .mp3 files stored in /sdcard/Music.
\end{itemize}}

\begin{itemize}
\item Precondition: 
\subitem Application is not running.
\subitem At least 6 .mp3 files are stored in /sdcard/Music.

\item Procedure:
\subitem Launch the application.

\item Postcondition:
\subitem The application launches the MusicPlayer Activity, ready to play.
\end{itemize}

\rule{\textwidth}{1pt}

\story{Obtain beats-per-minute for song.}{High}
{As a user, I, want the application to automatically obtain the beats-per-minute (BPM) of the .mp3 files located.}
{\begin{itemize}
\item Obtain 113 as BPM for Rick Astley's Never Gonna Give You Up, when locating the 12 .mp3 files stored in /sdcard/Music.
\item If no BPM is found for a song, it will not be playable.
\item I am able to manually set BPM for a song.
\end{itemize}}

\begin{itemize}
\item Precondition: 
\subitem Application is not running.
\subitem At least 6 .mp3 files are stored in /sdcard/Music.
\subitem One of the 6 .mp3 files are Rick Astley's Never Gonna Give You Up.
\subitem An internet connection is established.

\item Procedure:
\subitem Launch the application.
\subitem Locate Never Gonna Give You Up as current song, by pressing the \texttt{Next} button until this happens.

\item Postcondition:
\subitem Verify the BPM is 113.
\end{itemize}

\rule{\textwidth}{1pt}

\story{Navigate songs.}{High}
{As a user, I, want to be able to skip the current song, listen to the previously played song again. 
Further I want to be able to stop and/or pause the playing song.
It should also be possible to seek in the playing song.}
{\begin{itemize}
\item A \texttt{Next} button must exist, which skips to the next song.
\item A \texttt{Previous} button must exist, which skips to the previously played song.
\item A \texttt{Stop} button must exist, which stops the music.
\item A \texttt{Pause} button must exist, which pauses the music, so it can be resumed from the paused position.
\item A \texttt{SeekBar} must exist, which can seek in the playing song.
\end{itemize}}

\story{Keep playing when screen is off.}{High}
{ }
{\begin{itemize}
\item Criteria 1
\end{itemize}}

\story{Adjust music speed.}{Low}
{ }
{\begin{itemize}
\item Criteria 1
\end{itemize}}

\story{Seek in song.}{Low}
{ }
{\begin{itemize}
\item Criteria 1
\end{itemize}}



\subsection{Step Counter}
\story{Count the steps of the user.}{High}
{ }
{\begin{itemize}
\item Criteria 1
\end{itemize}}

\story{Calculate steps-per-minute of the user.}{High}
{ }
{\begin{itemize}
\item Criteria 1
\end{itemize}}

\story{Display steps-per-minute of the user.}{Low}
{ }
{\begin{itemize}
\item Criteria 1
\end{itemize}}



\subsection{Non-graphical Interface}
\story{Control while smartphone is on arm.}{High}
{ }
{\begin{itemize}
\item Criteria 1
\end{itemize}}